---
title: "FinalePackageLeman"
author: "Leman Binokay"
date: "10 01 2022"
output:
  pdf_document: default
  html_document: default
---

**INTRODUCTION**

This is an R package (FinalePackageLeman) document. FinalePackageLeman R package has 3 functions which are *is.all.unique*, *missing.NOs* and *product.of.the.others*.

**Function 1 - is.all.unique**

This function checks string, if it consists of different characters or not. It takes a string and splits its characters.Then,it compares length of the characters and length of the unique characters in a given string. After that, result is written as *all unique*, if the string consists of unique characters.
Result is written as *duplicates found*, if the string consists of same characters.

**R code**

```{r}

is.all.unique <- function(x){

  # Takes a string and splits its characters.
  # Unlist it to make the string turn into character by character
  string.split<-unlist(strsplit(x, ""))

  # Takes length of the characters to determine how many characters are in the given string.
  # Takes length of the unique characters to determine how many unique characters are in the given string.
  # Controls whether the length of the characters and unique characters are equal or not.
  if (length(string.split) == length(unique(string.split))){

    # Writes all unique if the length of the characters and unique characters are equal.
    cat("all unique")
  } else{

    # Writes duplicates found if the length the characters and unique characters are not equal.
    cat ("duplicates found")
  }
}


```

**Example**

```{r}
# x is a given string
x <-"leman"
is.all.unique(x)
# x is a given string
x <-"efe"
is.all.unique(x)
```
 
**Function 2 - missing.NOs**

This function finds missing numbers in a given list which consist of numbers between 1 to 100. It takes a list and finds missing numbers by using setdiff function.

**R code**

```{r}
# Defining the function, this function can find any removed number from the list.
# Takes a list and finds missing numbers by using setdiff function.

missing.NOs <- function(x) {setdiff(c(1:100), x)}
```

**Example**

```{r}
# x is a given list
x <- c(1:45,48:100)
missing.NOs(x)
```

**Function 3 - product.of.the.others**

This function products other numbers in a given vector and writes on it. It creates a vector which consists of missing values and has the same length with a given vector. Then, it makes a loop for each values in a vector. After that, it products of the numbers other then itself.

**R code**

```{r}
product.of.the.others <- function(x) {

  # Creates a vector which consists of missing values and has the same length with a given vector.
  PO <- rep(NA, length(x))

  # Makes a loop for each values in a vector.
  for (i in 1:length(x)) {

    # Products of the numbers other then itself.
    PO[i] <- prod(x[-i])
  }
  return(PO)
}
```

**Example**

```{r}
# x is a given vector
x <- c(1,2,3,4)
product.of.the.others(x)

```


